MS_CNuptake.Rmd

### 2022-10-19 MS_CNuptake.Rmd
small update

mod_nue3 <- (lm(nue~vpd_a+Tg_a+PPFD_a,data=nue_allplots))
summary(mod_nue3)
nue4c <- visreg(mod_nue3,"vpd_a",type="contrast")
nue6c <- visreg(mod_nue3,"Tg_a",type="contrast")
nue8c <- visreg(mod_nue3,"PPFD_a",type="contrast")

>>>>

mod_nue5 <- (lm(nue~vpd_a+Tg_a+PPFD_a,data=nue_allplots))
summary(mod_nue5)
nue4c <- visreg(mod_nue5,"vpd_a",type="contrast")
nue6c <- visreg(mod_nue5,"Tg_a",type="contrast")
nue8c <- visreg(mod_nue5,"PPFD_a",type="contrast")
